\vskip-0.6in \Large Political Uncertainty

### 2016-02-09 two-groups.tex
revised legislature portion of sec:solve

\vskip.3in
\section{Our Extension to Uncertainty}
General thoughts on extension to uncertainty
\begin{itemize}
	\item I think, without uncertainty, you would estimate $m^*$ as a function of the parameters of $v$ and WTP
		\begin{itemize}
			\item It's useful that $m^*$ is unique. Not clear it would extend to case of uncertainty, but I think it's likely so I'm going to assume it for now
		\end{itemize}
	\item I'm pretty sure  this predicts that $B$ should never pay anything when there is no uncertainty, but I don't see where they say it explicitly (I should read more carefully to verify)
		\begin{itemize}
			\item Uncertainty should reverse this, right?
			\item What is uncertainty? Make $v(z)$ stochastic is most natural
				\begin{itemize}
					\item I'm going to start with linear parameterization of $v(z)$ and add uncertainty. For now, take same form for $v(z)$
						\[
						  v(z) = \alpha -\beta \cdot z
						\]
						and take $z$ as a random variable distributed normally with mean $z$ and standard deviation $\sigma_z$. This is unfortunate nomenclature, since later we'll probably want to take this to a standard normal ``Z'' 
							\begin{itemize}
								\item This means that the legislators are ordered on the interval according to their ideal points, but there is acknowledged uncertainty surrounding their preferences 
								\item What is the source of this uncertainty? We take it to vary by legislator and also possibly by issue area when we extend the model to account for that
								\item Uncertainty comes from: \textbf{log-rolling and cross-pressuring; length of voting record; electoral incentives that we can't control for}
							\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}

\vskip.3in
\subsection{Solving the Model}
Backward induction (legislature moves last; B makes last bribe; A makes first bribe)
\begin{enumerate}
	\item Legislature
		\begin{itemize}
			\item Each legislator $z$ will decide whether to vote for $x$ or $s$ given $z$, $a(z)$ and $b(z)$. Votes for $x$ if
			  \[
				  v(z) = \alpha -\beta \cdot z + a(z) - b(z) > 0
				\]
				(whether the inequality is weak or strict depends on tie-breaking rules set out in the paper)
					\begin{itemize}
						\item Notice that a bribe from $B$ is subtracted because it makes the alternative \textit{less} attractive
					\end{itemize}
		\end{itemize}
	\item Vote buyer B
		\begin{itemize}
			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''
			\item This has to be adapted to our situation with uncertainty
				\begin{itemize}
					\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
					\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
					\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
					\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
					\item Some legislators who are past FOC point will not be lobbied
				\end{itemize}
		\end{itemize}	
\end{enumerate}

\newpage
\section{Discrete Model}
\begin{itemize}
	\item Note that this model \textit{may} introduce interdependence between the bid functions that does not exist in the continuous model
	\item What is not clear is whether this happens when the WTP constraint is not binding, which I'm going to assume from the start, and maybe impose later
	\item We write
	  \[
		  v(z) = \alpha -\beta z + \ve_z + a(z) - b(z)
		\]
			\begin{itemize}
				\item Note that we will have to worry about separately identifying the parameters. So for now, will assume $\ve$ does not vary in $z$
				\item Also going to ignore Vote Buyer A's choice for now, so we have
			\end{itemize}
	  \[
		  v(z) = \alpha -\beta z + \ve - b(z)
		\]
	\item Then the probability that legislator $z$ votes against the new proposal is
	  \[
		  \Pr\left[v(z)\leq 0 \right] = \Pr\left[\alpha -\beta z + \ve - b(z) \leq 0 \right] 
			                            = \Pr\left[\ve \leq \beta z - \alpha + b(z) \right] 
		\]
		Assuming $\ve \sim \text{Logistic} \ (0,1)$, the probability that legislator $z$ votes ``no'' is $\frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}$. 
	\item Take a model with three legislators with ideal points at $z=-\frac{1}{2}$, $z=0$ and $z=\frac{1}{2}$. For ease of notation, let
		\begin{enumerate}
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\label{page:sh}$ 

@@

	\item Then the three probabilities are
		\begin{itemize}
			\item $\frac{1}{1+e^{-\left(- \alpha + b(0) \right)}} = \frac{1}{1+e^{-X}}$, $\frac{1}{1+e^{-\left(\frac{\beta}{2}- \alpha + b(\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Y}}$, $\frac{1}{1+e^{-\left(-\frac{\beta}{2}- \alpha + b(-\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Z}}$
			\item Whether a legislator $z$ votes ``no'' is a random variable, denote it $X(z)$, distributed Bernoulli with this probability:
				\[
				  X(z) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}
				\]
			\item Need to max probability of at least two voting ``no'': $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$
			\item Thus, maximization problem for Vote Buyer B (in absence of Vote Buyer A) is
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(\frac{1}{2}\right)=0\right)  + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
				\end{multline}
			Substituting from the definition of $X$,
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \left(1-\frac{1}{1+e^{-Y}}\right)  + \\
					\frac{1}{1+e^{-Z}} \left(1-\frac{1}{1+e^{-X}}\right) \frac{1}{1+e^{-Y}} + \\
					\left(1-\frac{1}{1+e^{-Z}} \right) \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} + \\
					\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
				\end{multline}
			This can be simplified as 
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} +
					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-Z}} + \\
					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
					\label{eq:obj}
				\end{multline}

		\end{itemize}
	\item Some notes
		\begin{itemize}
			\item If we divide through by 2, the left side is the average minus the product
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
		\end{itemize}
	\end{itemize}

\subsection{Adding Vote Buyer A}

\subsection{Adding Non-negativity Constraints for Bribes}
The Lagrangian for the problem is the same as Expression~\ref{eq:obj}, adding on $\lambda_X b\left(0\right) + \lambda_Y b\left(\frac{1}{2}\right) + \lambda_Z b\left(-\frac{1}{2}\right)$

>>>>

\vskip.3in
\section{Our Extension to Uncertainty}
General thoughts on extension to uncertainty
\begin{itemize}
	\item I think, without uncertainty, you would estimate $m^*$ as a function of the parameters of $v$ and WTP
		\begin{itemize}
			\item It's useful that $m^*$ is unique. Not clear it would extend to case of uncertainty, but I think it's likely so I'm going to assume it for now
		\end{itemize}
	\item I'm pretty sure  this predicts that $B$ should never pay anything when there is no uncertainty, but I don't see where they say it explicitly (I should read more carefully to verify)
		\begin{itemize}
			\item Uncertainty should reverse this, right?
			\item What is uncertainty? Make $v(z)$ stochastic is most natural
				\begin{itemize}
					\item I'm going to start with linear parameterization of $v(z)$ and add uncertainty. For now, take same form for $v(z)$
						\[
						  v(z) = \alpha -\beta \cdot z
						\]
						and take $z$ as a random variable distributed normally with mean $z$ and standard deviation $\sigma_z$. This is unfortunate nomenclature, since later we'll probably want to take this to a standard normal ``Z'' 
							\begin{itemize}
								\item This means that the legislators are ordered on the interval according to their ideal points, but there is acknowledged uncertainty surrounding their preferences 
								\item What is the source of this uncertainty? We take it to vary by legislator and also possibly by issue area when we extend the model to account for that
								\item Uncertainty comes from: \textbf{log-rolling and cross-pressuring; length of voting record; electoral incentives that we can't control for}
							\end{itemize}
				\end{itemize}
		\end{itemize}
	\item Note that this model \textit{may} introduce interdependence between the bid functions that does not exist in the continuous model
	\item What is not clear is whether this happens when the WTP constraint is not binding, which I'm going to assume from the start, and maybe impose later
\end{itemize}

\newpage
\section{Solving the Model}
\label{sec:solve}
Backward induction (legislature moves last; B makes last bribe; A makes first bribe)
\begin{enumerate}
	\item Legislature
		\begin{itemize}
			\item Each legislator $z$ will decide whether to vote for $x$ or $s$ given $z$, $a(z)$ and $b(z)$. Votes for $x$ if
			  \[
				  v(z) = \alpha -\beta z + \ve_z + a(z) - b(z)
				\]
				(whether the inequality is weak or strict depends on tie-breaking rules set out in the paper)
					\begin{itemize}
						\item Notice that a bribe from $B$ is subtracted because it makes the alternative \textit{less} attractive
						\item Note that we will have to worry about separately identifying the parameters. So for now, will assume $\ve$ does not vary in $z$
					\end{itemize}
			\item Also going to ignore Vote Buyer A's choice for now, so we have
				\[
					v(z) = \alpha -\beta z + \ve - b(z)
				\]
			\item Then the probability that legislator $z$ votes against the new proposal is
				\[
					\Pr\left[v(z)\leq 0 \right] = \Pr\left[\alpha -\beta z + \ve - b(z) \leq 0 \right] 
			                            = \Pr\left[\ve \leq \beta z - \alpha + b(z) \right] 
				\]
				Assuming $\ve \sim \text{Logistic} \ (0,1)$, the probability that legislator $z$ votes ``no'' is $\frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}$.
			\item Take a model with three legislators with ideal points at $z=-\frac{1}{2}$, $z=0$ and $z=\frac{1}{2}$. For ease of notation, let
				\begin{enumerate}
					\item $X = -\alpha + b(0)$ 
					\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
					\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\label{page:sh}$ 
				\end{enumerate}
			\item Then the three probabilities are
				\begin{itemize}
					\item $\frac{1}{1+e^{-\left(- \alpha + b(0) \right)}} = \frac{1}{1+e^{-X}}$, $\frac{1}{1+e^{-\left(\frac{\beta}{2}- \alpha + b(\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Y}}$, $\frac{1}{1+e^{-\left(-\frac{\beta}{2}- \alpha + b(-\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Z}}$
					\item Whether a legislator $z$ votes ``no'' is a random variable, denote it $X(z)$, distributed Bernoulli with this probability:
						\[
							X(z) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}
						\]
				\end{itemize}
		\end{itemize}

\item Vote buyer B
		\begin{itemize}
			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''
			\item This has to be adapted to our situation with uncertainty
				\begin{itemize}
					\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
					\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
					\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
					\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
					\item Some legislators who are past FOC point will not be lobbied
				\end{itemize}
		\end{itemize}

			\item Need to max probability of at least two voting ``no'': $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$
			\item Thus, maximization problem for Vote Buyer B (in absence of Vote Buyer A) is
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(\frac{1}{2}\right)=0\right)  + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
				\end{multline}
			Substituting from the definition of $X$,
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \left(1-\frac{1}{1+e^{-Y}}\right)  + \\
					\frac{1}{1+e^{-Z}} \left(1-\frac{1}{1+e^{-X}}\right) \frac{1}{1+e^{-Y}} + \\
					\left(1-\frac{1}{1+e^{-Z}} \right) \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} + \\
					\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
				\end{multline}
			This can be simplified as 
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} +
					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-Z}} + \\
					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
					\label{eq:obj}
				\end{multline}

	\item Some notes
		\begin{itemize}
			\item If we divide through by 2, the left side is the average minus the product
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
		\end{itemize}

@@

\section{Adding Vote Buyer A}

\section{Adding Non-negativity Constraints for Bribes}
The Lagrangian for the problem is the same as Expression~\ref{eq:obj}, adding on $\lambda_X b\left(0\right) + \lambda_Y b\left(\frac{1}{2}\right) + \lambda_Z b\left(-\frac{1}{2}\right)$
